### 2023-10-02 3.Design/genwei.tex
Bunch of changes moving to bu

The choice for the weight generation was to use Keras API with the tensorflow framework. However, both tensorflow and pyTorch were tried and were giving similar results, the final choice of using tensorflow was made because it's the most popular among the research group.

Generating the weights simply requires to train the \ac{NN} with the wanted achitecture. Once the trainning is done, we can run an inference of the \ac{NN} to check whether the training was good. This step is very important and allows to perfect the \ac{NN}. Once a correct architecture has been found, the weights are reorganized based the same model required by the netlist generator (\cref{sec:netlist}) and saved in a file along with a quick description of the architecture used for generating those weights for an easier generation of the netlist(\cref{sec:netlist}). The files can now be taken and used to generate the netlist.

The code used for all the weights generations is available at \cite{lstmWei}.

>>>>

The choice for the weight generation was to use Keras API with the tensorflow framework. However, both tensorflow and pyTorch were tried and were giving similar results, the final choice of using tensorflow was made because it's the most popular among the research group.%INESC ID ???

\subsection{Training the weights}

Generating the weights requires to train a \ac{NN}. This is done in Keras by creating the model, in other words the architecture required to solve the problem. This model contains the description of the \ac{NN}, such as the type of \ac{RNN} and the Dense layers that would come before of after the \ac{RNN}. In Keras, there are only two of the \ac{LSTM} variants (\cref{sec:lstm}) available :

\begin{itemize}
\item The \ac{NP} \ac{LSTM} : This is most commonly used version and by such one of the two available in Keras.
\item The \ac{GRU} : This one is present here because it's considered to be different from an \ac{LSTM} \ac{NN} despite their similarities.
\end{itemize}

The other kinds of \ac{LSTM} are not present in the default Keras librairies.

Training can only be done outside of the circuit as this state of the project. However, in order to train the weights as closely as they would have been on a real circuit, the activation functions used for the training are the custom activation functions generated by the dedicated circuit (\cref{sec:af}). In other words, the activation functions used are the ones shown in \cref{fig:afGraph}. This allows to train the weights as they almost (considering the activation functions are recreated using 51 points) as they would have been in the real circuit.

All the training are done using \ac{MSE} loss function and Adam optimizer \cite{adamOpti}.

\subsection{Exporting the weights}

Once all the parameters (number of hidden states, number of dense layers, etc) have been set. The weights can be exported using the required weight

Once a correct architecture has been found, the weights are reorganized based the same model required by the netlist generator (\cref{sec:netlist}) and saved in a file along with a quick description of the architecture used for generating those weights for an easier generation of the netlist(\cref{sec:netlist}). The files can now be taken and used to generate the netlist.

The code used for all the weights generations is available at \cite{lstmWei}. %TODO README

### 2023-10-02 3.Design/netlist.tex
Bunch of changes moving to bu

The weights are stored in a single file that is the save a numpy array. The first dimension contains the weights for the different layers. Depending on the layer used, the weights are stored a bit differently :

\begin{itemize}
  \item Dense layer : This is basically a \ac{VMM} so the weights are just sorted linearly in a list. The list is of size $n^2$, where $n$ is the size of the input vector. \Cref{mtrx:wei} shows the position ($i$) of the weight ($w_i$) in the matrix.
  \item \ac{LSTM} layer : An \ac{LSTM} layer contains four \acp{VMM} which can be assimilated and thus stored like a dense layer. The weights for each \ac{VMM} is then stored in a sub list.
\end{itemize}

>>>>

The weights are stored in a single file that is the save a numpy array. This file also contains a brief description of the architecture being used. The first index stores this desciption. the following indexes are for the actual weights, in the order given in the description. Depending on the layer used, the weights are stored a bit differently :

\begin{itemize}
  \item Dense layer : This is basically a \ac{VMM} so the weights are just sorted linearly in a list. The list is of size $n^2$, where $n$ is the size of the input vector. \Cref{mtrx:wei} shows the position ($i$) of the weight ($w_i$) in the matrix. This is represented in the description as "Dense($n_o$)" where $n_o$ is the number of output
  \item \ac{LSTM} layer : An \ac{LSTM} layer contains four \acp{VMM} which can be assimilated and thus stored like a dense layer. The weights for each \ac{VMM} is then stored in a sub list.
\end{itemize}
